---
title: "assignment1"
description: |
  A short description of the post.
author:
  - name: Benno Kass
    url: https://example.com/norajones
date: 04-18-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#first load the libraries we'll need
library(tidyverse)
library(plotly)
library(nycflights13) # <- make sure to install this package 


```

## Functions

1. Create a function that will return the sum of 2 numbers.

```{r}

add <- function(a,b){
  return(a+b)
}

add (3,2)


```


2. Create a function that will return the mean of a vector of numbers fed to it.  
A sample vector of values is provide here to help.

```{r}

mynumbers <- sample(1:100, 10)

mymean <- function(vec){
  return(mean(vec))
}

mymean(mynumbers)

```


3. Now, expand on the function you made above, and instead of just returning the number, have it return the sentence:  
"The mean is ___" where the blank is the calculated result.

```{r}

mymean <- function(vec){
  return(paste("The mean is", mean(vec)))
}

mymean(mynumbers)



```


```{r}
#load the data to use for the rest of the assignment questions
flights <- nycflights13::flights

```

4. Using the `flights` dataset from the package `nycflights13` loaded in the above cell, create a function that filters the data frame to only include records from a single originating airport (column name `origin`).

```{r}

filterairport <- function(df,airport){
  return(df[df$origin==airport,])
}

flights %>% filterairport("EWR")





```


5. Similarly, using the `flights` dataset, create a function that:  
- filters the data frame to only include records from a single originating airport (column name `origin`), and then  
- aggregates the results by airline (`carrier`) to show how many flights each airline has from that airport.

```{r}


getnumflightsforairport <- function(df,airport){
  return(df[df$origin==airport,] %>% group_by(carrier) %>% count())
}

flights %>% getnumflightsforairport("EWR")







```


6. Similarly, using the `flights` dataset, create a function that:  
- filters the data frame to only include records from a single originating airport (column name `origin`), and then  
- filter to only include flights longer than a specific number of minutes (`air_time`), and then  
- aggregates the results by airline (`carrier`) to show how many flights of that length each airline has from that airport.

```{r}



getnumflightsforairportlongerthantime <- function(df,airport,time){
  return(df[df$origin==airport,] %>% filter(air_time>time) %>%  group_by(carrier) %>% count())
}

flights %>% getnumflightsforairportlongerthantime("EWR",124)




```



## Plotly charts

7. Using the `flights` dataset, use plotly to create a bar chart showing the breakdown of flights by airline that originate
from JFK airport (`origin`) and are more than 400 minutes in length (`air_time`).

```{r}

result <- flights %>% getnumflightsforairportlongerthantime("JFK",400)

plot_ly(
  x=result$carrier,
  y=result$n,
  name="JFK flight",
  type="bar"
)




```


8. Using the `flights` dataset, use plotly to create a bar chart showing which destination airports (`dest`) have the most
flights with durations of over 400 minutes (`air_time`).

```{r}
results <- flights %>% filter(air_time>400) %>% group_by(dest) %>% count()
plot_ly(
  x=results$dest,
  y=results$n,
  type="bar",
)





```


9. Using the `flights` dataset, use plotly to create a donut chart showing the share of flights each airline has for 
flights with a destination of Daniel K. Inouye International Airport (HNL) in Honolulu.

```{r}
results<-flights %>% filter(dest=="HNL") %>% group_by(carrier) %>% count()
results %>% plot_ly(labels=~carrier,values=~n) %>% add_pie(hole=0.6)





```


10. Using the `flights` dataset, use plotly to create a scatterplot chart for flights with a destination of 
Daniel K. Inouye International Airport (HNL) in Honolulu, that shows the relationship between the departure delay (`dep_delay`) and arrival delay (`arr_delay`).

```{r}
results <- flights %>% filter(dest=="HNL")

results %>% plot_ly(x=~dep_delay,y=~arr_delay)



```

